OSF management

### 2021-02-01 osf/manage-osf.Rmd
:bento: - update trial lists for osf

for (file in 2:nrow(old_tgs)) {
  osf_rm(old_tgs[file,], check = FALSE)
}

@@

>>>>

for (file in 1:nrow(old_tgs)) {
  osf_rm(old_tgs[file,], check = FALSE)
}

@@

# Trial lists

```{r tlists}
tlists <- list.files("./data/trial-lists", ".csv", full.names = TRUE)
typ <- read_csv("./data/dataset/typicality.csv")

for (tlist in tlists) {
  speaker <- str_sub(tlist, 20, 21)
  tbl <- read_csv(tlist) %>%
    mutate(
      speaker = speaker,
      trial = row_number()
    ) %>%
    left_join(y = typ) %>%
    select(speaker, trial, condition, typicality, everything())

  write_csv(tbl, file = paste0("./osf/data/production/trial-lists/", speaker, ".csv"))
}
```

```{r tlists-upload}
trials <- osf_ls_files(data_comp, "production", pattern = "trial-lists")

# delete old trials
old_trials <- osf_ls_files(trials, pattern = ".csv", n_max = Inf)

for (file in 1:nrow(old_trials)) {
  osf_rm(old_trials[file,], check = FALSE)
}

# upload new trials
new_trials <- list.files("./osf/data/production/trial-lists/", ".csv", full.names = TRUE)

for (trial in new_trials) {
  osf_upload(
    trials,
    path = trial,
    conflicts = "overwrite", verbose = T
  )
}
```
